Tool-driven Revolutions in Archaeological Science

### 2018-11-16 analysis/paper/jcaa-paper.Rmd
add something on gieryn

As @Galison_1997 describes a shift in the practices of physicists, so does archaeological practice change in the digital age. What exactly this entails, is diverse and has been discussed more thoroughly by @Huvila_2018 who talk about what questions on archaeological practices and knowledge work should be answered to avoid a technologically determisitic approach to computational archaeology.

>>>>

As @Galison_1997 describes a shift in the practices of physicists, so does archaeological practice change in the digital age. @Huvila_2018 have explored the use of digital tools on archaeological practices to understand the boundaries of what counts as archaeological, what is  merely related to archaeology and what should be excluded from archaeology. Reflecting on @Huvila_2018, our view is the use use of code is unquestionably archaeology, since it is just one of many tools that archaeologists are using for converting raw data into summaries, visualisations, and insights.

These concerns about how digital tools affect what we consider is and isn't archaeology intersect with the work of @gieryn1999cultural on boundary construction. In his cultural cartography of science, Gieryn examines boundaries between science generally and varieties of less authoritative non-science. He argues that the boundaries are drawn and redrawn contiuously in inflexible, historically changing and sometimes ambiguous ways. Gieryn claims that the cultural authority of science flows from boundary work in professional and political settings where scientists construct a public image for science as a source of credible knowledge, validate their work, and marginalize claims by competitors. Boundary work involves attributions of selected characteristics to science in order to distinguish it from non-scientific competitors. The increasing voluntary use and sharing of code by researchers, and demands for it by readers and peer reviewers is a form of active boundary work that is shifting the boundary between scientific and non- or less-scientific archaeology. We argue that the use of code as a research tool, and sharing of code as a public research product, are increasingly attributes that are being used to distinguish science from less scientific work.  The reason is because using code, and making available for others to inspect, enhancing the credibility of knowledge claims.
